Graphical Tests for Power Comparison of Competing Designs

### 2012-03-28 intro.tex
working on intro, added/fixed references

% !TEX root = comparison.tex
%% \section{Introduction} %for journal use above \firstsection{..} instead
%We introduce and discuss a tool for comparing different charts that are renderings of the same data in order to evaluate them for efficiency.
So, you've just spent countless hours, burning the late night candle
wax, and discovered several astonishing features in the data. Your
exploratory graphics are quick to produce, interactive, flexible,
fabulous for discovery, but now you need to present the information to
your boss, the co-workers, a class of students, or get it published in
that top-rated journal. Those exploratory graphics are unlikely to
communicate the information to your audience efficiently.
%Graphics have a central role in the discovery process as well as in the presentation of results. As designer of  charts one of our main goals is to display data so that the information it contains is relayed in the most efficient way. 
In deciding on the best presentation display %out of the seemingly endless multitude of methods
we will guided by past experience, aesthetic preferences, and knowledge of general perceptual strengths and weaknesses determined from data graphics user studies such as \citet{cleveland:1984} and the large MTurk study in \citet{heer:2010}. But it is hard to take these general principles and apply them to specific visual communication task, especially in an objective manner.

>>>>

% !TEX root = comparison.tex
%% \section{Introduction} %for journal use above \firstsection{..} instead
%We introduce and discuss a tool for comparing different charts that are renderings of the same data in order to evaluate them for efficiency.
So, you've just spent countless hours, burning the late night candle
wax, and discovered several astonishing features in the data. Your
exploratory graphics are quick to produce, interactive, flexible,
fabulous for discovery, but now you need to present the information to
your boss, the co-workers, a class of students, or get it published in
that top-rated journal. Those exploratory graphics are unlikely to
communicate the discovered information to your audience efficiently,
or elegantly.  To decide on the best way to present the specific
information there can be many types of plots to choose from. The
decision process is assisted by past experience, personal aesthetic
preferences, the characteristics of the audience, and a good working
knowledge of general perceptual strengths and weaknesses
\citep{cleveland:1984,heer:2010}. Perceptual studies are thinly spread
for data visualization, and have, and will probably, only cover very
broad perceptual principles. Faced with design decisions for a very
specific task requires a closer level of detail. Focus groups
\citep{Mazza07} can find small problems with designs and move us
closer to a final handful of possible designs, but they lack broad
audience validatity and objective evaluation.

%determined from data graphics user studies such as \citet{cleveland:1984} and the large MTurk study in \citet{}. But it is hard to take these general principles and apply them to specific visual communication task, especially in an objective manner.
